Appendix

### 2019-07-19 figures/07_model-selection.Rmd
presentation edits

```{r tn_re_compare, fig.height=3}
# compare lakes in signif hu4s
dt        <- readRDS("../data/dt_scaled.rds") %>%
  mutate(signif_hu4 = hu4_zoneid %in% signif_hu4_ids) %>%
  tidyr::gather(key = "key", value = "value", 
                      -lagoslakeid, -hu4_zoneid, -hu12_zoneid, -signif_hu4) %>%
  group_by(key, signif_hu4) %>%
  mutate(median = median(value, na.rm = TRUE))

dt_predictors <- dplyr::filter(dt, key %in% 
                                 c("tp",
                                   "nitrogen_atmospheric_deposition",
                                   "clay_pct")) %>%
  dplyr::left_join(pred_key, by = c("key" = "var"))
dt_predictors[is.na(dt_predictors$pretty), "pretty"] <- 
  sapply(dt_predictors[is.na(dt_predictors$pretty), "key"], toupper)

>>>>

```{r tn_re_compare, fig.height=3, fig.width=4}
# compare lakes in signif hu4s
dt        <- readRDS("../data/dt_scaled.rds") %>%
  mutate(signif_hu4 = hu4_zoneid %in% signif_hu4_ids) %>%
  tidyr::gather(key = "key", value = "value", 
                      -lagoslakeid, -hu4_zoneid, -hu12_zoneid, -signif_hu4) %>%
  group_by(key, signif_hu4) %>%
  mutate(median = median(value, na.rm = TRUE))

dt_predictors <- dplyr::filter(dt, key %in% 
                                 c(#"tp",
                                   "nitrogen_atmospheric_deposition",
                                   "clay_pct")) %>%
  dplyr::left_join(pred_key, by = c("key" = "var"))
dt_predictors[is.na(dt_predictors$pretty), "pretty"] <- 
  sapply(dt_predictors[is.na(dt_predictors$pretty), "key"], toupper)

### 2019-07-19 manuscript/appendix.Rmd
presentation edits

ggplot(dt_waffle,
       aes(fill=`Trophic State`, values = `value`)) +
  geom_waffle(color = "white", size=0.7, n_rows = 5, flip = TRUE) +
  # facet_wrap(~key, ncol = 1) +
  scale_x_discrete(expand = c(0,0)) +
  scale_y_discrete(expand = c(0,0)) +
  shades::lightness(scale_fill_brewer(palette = "Greens", type = "seq"), 
                    shades::delta(-10)) +
  coord_equal() +
  theme_enhance_waffle() + 
  theme(strip.background = element_blank(), 
        rect = element_rect(fill = "transparent"), 
        legend.position = "bottom", 
        title = element_blank(), 
        strip.text = element_text(size = 16), 
        legend.text = element_text(size = 10), 
        legend.key.size = unit(0.5, "line")) + 
  guides(fill = guide_legend(nrow = 2))

>>>>

ggplot(dt_waffle,
       aes(fill=`Trophic State`, values = `value`)) +
  geom_waffle(color = "white", size=0.7, n_rows = 10, flip = TRUE) +
  # facet_wrap(~key, ncol = 1) +
  scale_x_discrete(expand = c(0,0)) +
  scale_y_discrete(expand = c(0,0)) +
  shades::lightness(scale_fill_brewer(palette = "Greens", type = "seq"), 
                    shades::delta(-10)) +
  coord_equal() +
  theme_enhance_waffle() + 
  theme(strip.background = element_blank(), 
        rect = element_rect(fill = "transparent"), 
        legend.position = "bottom", 
        title = element_blank(), 
        strip.text = element_text(size = 16), 
        legend.text = element_text(size = 10), 
        legend.key.size = unit(0.5, "line")) + 
  guides(fill = guide_legend(nrow = 2))
